\section{Building The Corpora}

The natural first step was to look at other corpora that aggregate similar data.  

The \textbf{Europarl} dataset \cite{koehn_europarl_2005} aggregates proceedings of the European Parliament in twenty-one different European languages\footnote{All 21 Europarl languages: Romanic (French, Italian, Spanish, Portuguese, Romanian), Germanic (English, Dutch, German, Danish, Swedish), Slavic (Bulgarian, Czech, Polish, Slovak, Slovene), Finno-Ugric (Finnish, Hungarian, Estonian), Baltic (Latvian, Lithuanian), and Greek.} with the goal of generating sentence-aligned text for statistical machine learning translation systems. The overall structure is akin to a collection of plaintext with minimal tagging.

\textbf{ItaParlCorpus} \cite{cova_new_2025}, on the other hand, is a comprehensive, annotated, and machine-readable database of Italy's parliamentary speeches spanning from 1948 to 2022. Each speech is identified by a precise date, the role of the speaker, their party name and family, and the legislature number. It is not, however, very rich in terms of linguistic processing tagging.

\textbf{IMPAQTS} \cite{cominetti_impaqts_2024} is a multimodal corpus of around 2.65 million tokens, including 1,500 speeches uttered by 150 prominent politicians, spanning from 1946 to 2023. For each speaker, the corpus contains 4 parliamentary speeches, 2 rallies, 1 party assembly, and 3 statements (in person or broadcasted). The goal is to annotate political rhetoric that hides a deeper meaning, for example by employing sarcasm. There are four main types of annotation: implication (conventional, generalized, etc.), presupposition (e.g., pragmatic), vagueness (syntactic, semantic, metaphoric), and topicalization (either syntactic or prosodic).

\textbf{Parola di Leader}, and specifically the corpus LP4 \cite{giuliano_il_2019}, is a corpus of more than five million occurrences taken from the stenographic archives of the Chamber of Deputies of Italy\footnote{Chamber of Deputies official online public archive: \url{https://legislatureprecedenti.camera.it/}.}, between 1948 (first legislature of the Italian Republic) and 2011 (excluding the Monti Government, the $61^{st}$ legislature).

They selected a list of thirty "highly influential politicians"\footnote{The full list of politicians follows: Giorgio Almirante, Giuliano Amato, Giulio Andreotti, Enrico Berlinguer, Silvio Berlusconi, Pier Luigi Bersani, Fausto Bertinotti, Rosy Bindi, Emma Bonino, Umberto Bossi, Pier Ferdinando Casini, Francesco Cossiga, Bettino Craxi, Massimo D'Alema, Alcide De Gasperi, Ciriaco De Mita, Antonio Di Pietro, Amintore Fanfani, Gianfranco Fini, Ugo La Malfa, Aldo Moro, Pietro Nenni, Achille Occhetto, Marco Pannella, Romano Prodi, Giuseppe Saragat, Giovanni Spadolini, Palmiro Togliatti, Valter Veltroni, Nichi Vendola.} and then for each of them they selected some speeches. Overall, they collected 1877 distinct speeches.

The corpus could be considered a collection of thirty distinct corpora, one for each politician. Each of these has, among others, the following features: name of the politician, role of the politician (for example, Prime Minister), whether the politician is in the majority party or in the opposition, legislature number and sitting number of the day, date of the sitting, topic of the speech, name of the current Government (e.g., \textit{Berlusconi I}), and lastly a reference to the file that holds the actual speech.

There is also a corpus for the vocabulary that holds, for each word, the total number of occurrences, a part-of-speech\footnote{In grammar, a part of speech or part-of-speech (abbreviated as POS or PoS) is a category of words (or, more generally, of lexical items) that have similar grammatical properties \cite{payne_describing_1997}.} tag, its lemma, a count for the number of occurrences for each politician, majority party and opposition, and lastly the imprinting tag (e.g., masculine singular).

Lastly, \textbf{ParlaMint} \cite{erjavec_parlamint_2023,erjavec_parlamint_2025} is a compiled collection of comparable parliamentary corpora for a number of countries and languages. ParlaMint corpora are interoperable, i.e. encoded to a very constrained common ParlaMint schema, a specialization of the Parla-CLARIN\footnote{Parla-CLARIN, a TEI schema for corpora of parliamentary proceedings: \url{https://clarin-eric.github.io/parla-clarin/}.} recommendations, which are a customization of the TEI Guidelines\footnote{P5 TEI Guidelines: \url{https://tei-c.org/guidelines/p5/}.}.

It is a collection of parliamentary sittings split into utterances. An example of two utterances could be \textit{Politician: "I ask permission to speak."}, \textit{President of the Senate: "Permission granted."}. For each utterance there are, among others, the following metadata: an ID for both the whole sitting and the utterance itself, a title of the sitting, a date of the sitting, the State Body where it took place (e.g., the Senate of the Republic), the name of the speaker and their affiliation, as well as the name of their coalition. 

Speeches are collected before being split into their own datasets, and for each speech we have, among others, a unique ID and a date, the type of speech (e.g., \textit{Interview} or \textit{Rally}), the venue channel (e.g., \textit{BBC News}), the unique ID of the speaker and their role (e.g., \textit{host} or \textit{main speaker}), the text of the speech itself and its type (e.g., \textit{Question}, \textit{Answer}, \textit{Interruption}) and whether there have been any \textit{Incidents} and their types.

Incidents are breaks in the flow of the conversation, and they can be of different types\footnote{Full list of incident types: "action", "incident", "leaving", "entering", "break", "pause", "sound", "editorial".}, for example \textit{"leaving"} or \textit{"break"}. If an incident is of the kinesic type, it can be further subdivided into different kinesic types, such as \textit{"applause"} or \textit{"laughter"}\footnote{Full list of kinesic types: "kinesic", "applause", "ringing", "signal", "playback", "gesture", "smiling", "laughter", "snapping", "noise".}. If the incident is of the vocal type, it can be further subdivided into different vocal types, such as \textit{"question"} or \textit{"shouting"}\footnote{Full list of vocal types: "greeting", "question", "clarification", "speaking", "interruption", "exclamat", "laughter", "shouting", "murmuring", "noise", "signal".}.

Speakers and Parties also have their own datasets, with unique IDs, names, affiliations, roles and the like.

Overall, the taxonomy of ParlaMint is strongly codified, which makes the dataset machine-readable and easier to interpret. All data is also saved in XML format.

\subsection{My Own Corpora}

Ultimately, I did not manage to find any corpus that I could directly integrate or use for my purposes, but I took inspiration from ParlaMint for the overall structure. 
At the time of writing, the corpus is not yet compiled, so the structure may change. The structure for the Italian corpus is the only one present at the moment. The structure is explained as tables and columns (or \textit{features}) of said tables.

Italian Government Table:
\begin{itemize}
    \item Column \textit{government}:
    \begin{itemize}
        \item e.g., \texttt{degasperi2}: "De Gasperi II";
        \item e.g., \texttt{spadolini1}: "Spadolini I";
        \item e.g., \texttt{forlani}: "Forlani";
    \end{itemize}
    \item Column \textit{primeMinister}:
    \begin{itemize}
        \item e.g., \texttt{degasperi}: \texttt{prime\_ministers.id==degasperi};
    \end{itemize}
    \item Column \textit{dateStart}: ISO 8601 (YYYY-MM-DD);
    \item Column \textit{dateEnd}: ISO 8601 (YYYY-MM-DD);
    \item Column \textit{legislature}:
    \begin{itemize}
        \item e.g., \texttt{1}: "I Legislatura";
        \item e.g., \texttt{15}: "XV Legislatura";
    \end{itemize}
    \item Column \textit{pm\_party}: The political party of the Prime Minister;
    \item Column \textit{gov\_leaning}: The political leaning of the specific government.
\end{itemize}

Prime Ministers Table:
\begin{itemize}
    \item Column \textit{pm\_ID}:
    \begin{itemize}
        \item e.g., \texttt{degasperi};
        \item e.g., \texttt{draghi};
        \item e.g., \texttt{meloni};
    \end{itemize}
    \item Column \textit{pm\_name}:
    \begin{itemize}
        \item e.g., \texttt{Alcide};
        \item e.g., \texttt{Mario};
        \item e.g., \texttt{Giorgia};
    \end{itemize}
    \item Column \textit{pm\_familyName}:
    \begin{itemize}
        \item e.g., \texttt{De Gasperi};
        \item e.g., \texttt{Draghi};
        \item e.g., \texttt{Meloni};
    \end{itemize}
    \item Column \textit{pm\_birthDate}: The birth date of the Prime Minister;
    \item Column \textit{pm\_deathDate}: The death date of the Prime Minister.
\end{itemize}

The dataset will have a structured taxonomy; for example, the political leaning will be codified as follows: 
\begin{itemize}
    \item \texttt{mixed}: e.g., CLN\footnote{The National Liberation Committee (Italian: Comitato di Liberazione Nazionale, CLN) was a political umbrella organization and the main representative of the Italian resistance movement fighting against the occupying forces of Nazi Germany and the fascist collaborationist forces of the Italian Social Republic. It was composed of Christian Democrats, Socialists, Communists, and Liberals.}, Pentapartito\footnote{The Pentapartito was the coalition government of five Italian political parties that formed between June 1981 and April 1991. It was composed of Christian Democrats, Social Democrats, Liberal Democrats, and Conservative Liberals.};
    \item \texttt{RR}: Far-Right;
    \item \texttt{LL}: Far-Left;
    \item \texttt{right}: Right;
    \item \texttt{left}: Left;
    \item \texttt{center}: Center;
    \item \texttt{centerRight}: Center-Right;
    \item \texttt{centerLeft}: Center-Left.
\end{itemize}