\section{Social Networks}

Broadly speaking, the goal of this mini-project is to gather a corpus of politicians' speeches and perform linguistic analyses on it. The idea is to start from standard NLP tasks such as word frequency and text complexity, to then move to classification tasks such as sentiment analysis and hate speech detection.

This objective is why I ultimately decided to gather a corpus of \textit{external speeches} rather than internal ones. Large language models are trained with tokenizers, and the resulting token distribution is highly imbalanced: Chung et al. \cite{chung_exploiting_2025} did a controlled study that scaled the vocabulary of the language model from 24K to 196K while holding data, computation, and optimization unchanged. They discovered that models are disproportionately optimized on the part of language that appears most often, meaning they are way better at understanding common words and patterns. This translates to the fact that internal speeches are less understandable for an AI agent. 

As previously stated, external speeches include social network communications. While television is still the first source of information for the majority of the population, online platforms are steadily growing and are already the preferred media for young people \cite{eurobarometer_media_2023,maher_twice_2024}. There is evidence of an increase in political participation due to social media usage, as well as risks for the functioning of democracy \cite{lorenz-spreen_systematic_2023,amsalem_people_2023}, and there have been attempts to predict election results with social media data analyses. Rita et al. measure sentiment polarity on Twitter, and conclude that tweets' sentiment is not a reliable election results predictor. Additionally, results also show that it is impossible to state that social media impacts voting decisions \cite{rita_social_2023}. 

Opposite results can be seen in Belcastro et al.'s \cite{belcastro_analyzing_2022} 2022 study: a real-time analysis was carried out during the 2020 US presidential election campaign, correctly identifying the leading candidate before Election Day in 10 out of 11 swing states.

Silva et al. \cite{silva_politicians_2022} managed to match tweets against parliamentary speeches to measure politicians' sentiment on a specific topic. They find that parliament members who participate less in parliamentary debate tend to have larger differences with their party on Twitter, suggesting that a certain level of self-censoring is taking place in the parliamentary arena.

That being said, X is just one channel among many used to connect with the voters: official messages to the nation, interviews, and public speeches are still powerful tools, and are often made publicly available in video format by the politicians themselves on their Facebook page and YouTube channel.
