 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\usepackage{fontawesome5}
\usepackage{xcolor}


\moderncvcolor{red} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\definecolor{venetianred}{HTML}{A42A04} 
\colorlet{color1}{venetianred} % main accent color \colorlet{color2}{mycolor!70} % secondary (slightly lighter)


%\colorlet{color2}{mycolor!70} % secondary (slightly lighter)

%\definecolor{color1}{HTML}{434C98}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=10mm,
 right=10mm,
 top=20mm,
 bottom=20mm,
 }


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Marco} % Your first name
\familyname{Bellò} % Your last name


\mobile{+393497617003}
 % Phone number
\email{marco.bello.vi@gmail.com} % Email ID



%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Marco Bellò} \\ \vspace{5pt}
    \small \faMobile* +39 3497617003 \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:marco.bello.vi@gmail.com}{marco.bello.vi@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faGithub \hspace{2pt} \href{https://github.com/mhetacc}{github.com/mhetacc} \hspace{1pt} $|$
    \hspace{1pt} \faTelegram \hspace{2pt} \href{https://t.me/mhetac}{t.me/mhetac}
    \\ \vspace{-3pt}
\end{center}
\vspace{10pt} % adjust spacing as needed

{\color{venetianred} \hrule height 0.8pt}

\vspace{10pt}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}


\cventry{2023--Current}{Master in Computer Science}{\textit{University of Padua}}{Padua, Italy}{}{}
%\cvlistitem{}

\cventry{2025}{Erasmus Exchange}{\textit{University of Helsinki}}{Helsinki, Finland}{}{}

\cventry{2023}{Bachelor in Computer Science}{\textit{University of Padua}}{Padua, Italy}{91/110}{}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\cventry{2026}{Regression and Classification Tasks in R}{}{}{}{Small-scale projects for both regression and classification tasks in R.}
\cvlistitem{\href{https://github.com/mhetacc/UNIPD_DataMiningClassificationRegression}{Repository: \texttt{mhetacc/UNIPD\_DataMiningClassificationRegression}}}
\cvlistitem{\href{https://github.com/mhetacc/UNIPD_DataMiningClassificationRegression/blob/0f0573f87e24efd75f3ae55be952e75852f156de/report/report.pdf}{PDF Report: \texttt{mhetacc/UNIPD\_DataMiningClassificationRegression/report.pdf}}}

\cventry{2025}{Pygame Showcase of Raft Consensus Algorithm}{}{}{}{Bare-bones Travian clone made in Pygame that showcases some of the Raft consenus algorithm's base functionality. The project leverages multithreading and remote procedure calls to achieve the desired results.}
\cvlistitem{\href{https://github.com/mhetacc/Raftian}{Repository: \texttt{mhetacc/Raftian}}}
\cvlistitem{\href{https://github.com/mhetacc/Raftian/blob/62ea393921eda52a92554dd10b958c9e5a53520d/docs/report/report.pdf}{PDF Report: \texttt{mhetacc/Raftian/.../report.pdf}}}

\cventry{2025}{Interactive Data Visualizer}{}{}{}{Visualize Europe's political leaning by state from 2009 to 2024. All data were taken from Eurostat official databases. The visualization, made with Plotly, consists of a map of Europe where each state is coloured based on its election results, and a line chart which shows three metrics: net earnings, immigration and poverty risk.}
\cvlistitem{\href{https://github.com/mhetacc/HLSK_InteractiveVisualizer}{Repository: \texttt{mhetacc/HLSK\_InteractiveVisualizer}}}

\cventry{2024}{Social Network Analysis on TikTok}{}{}{}{The goal was to measure the presence of echo chambers in the US political landscape. Ten politically relevant TikTok accounts have been selected, respectively five left-leaning and five right-leaning. Then, data from said accounts were collected to measure their activity and perform a social network analysis on their followers.}
\cvlistitem{\href{https://github.com/mhetacc/TikTok_SocialNetworkAnalysis}{Repository: \texttt{mhetacc/TikTok\_SocialNetworkAnalysis}}}
\cvlistitem{\href{https://github.com/mhetacc/TikTok_SocialNetworkAnalysis/blob/8dda0499f91e5cfa76714df77f055aa0956abfd0/Report_BelloMorini.pdf}{PDF Report: \texttt{mhetacc/TikTok\_SocialNetworkAnalysis/report.pdf}}}


%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	PROFILE% SECTION
%---------------------------------------------------------------------------------------%-%

%\section{Profiles}

%\cvitem{GitHub}{\url{https://github.com/sakshib}}
%\cvitem{clubVA}{\url{https://www.clubva.com/public/employee/avatar/index/Sakshi}\newline{}}

\section{Experience}

\cventry{2016--Current}{Private Tutoring}{}{}{}{I have been tutoring students aged eight to twenty-five for ten years, mainly in computer science.}


\cventry{2022}{Software Engineering Internship - Bachelor Thesis}{}{}{}{Implemented Augmented Reality features for a cross-platform mobile application developed in Flutter. The internship was completed at \href{https://datasoil.it/en/}{Datasoil s.r.l.}}

\cvlistitem{\href{https://github.com/mhetacc/tesi_triennale/blob/33390b38d2449843fecf2dcca12c471b4326e752/pdf/Tesi.pdf}{PDF Thesis (Italian): \texttt{mhetacc/.../Tesi.pdf}}}

\cventry{Summer 2023}{Janitor in preschool}{}{Vicenza}{}{}

\cventry{2017-2018}{Food Delivery}{Cosatiporto}{Vicenza}{}{}

\section{Skills}

%\cvitem{Subjects}{Operating Systems, DBMS, Compiler Design, Computer Networks, Pattern Recognition, Software engineering, Graph Theory, Algorithms, Microprocessors, Data Structures, Computer graphics, Digital Logic, Electronic Ciruits}%
\cvitem{Languages}{Italian (native), English (C1 - TOEFL 108/120)}

\vspace{1mm}

\cvitem{CS Skills}{Python, R, C++, Dart, Java, SQL, HTML, \LaTeX, Git, QML, GDScript. I'm comfortable with any desktop operating system. My current setup runs Fedora Workstation 43.}

\vspace{1mm}

\cvitem{Driving licenses}{A and B licences.}


\end{document}
